Robots, Are They Overlords or Serf-Laborers?

### 2015-06-13 draft1.tex
Edit the Legal and Ethical Issues section

\subsection{Legal and Ethical Issues}
Robots are envisioned to be controlled by a such intelligence which enable their to perceive their surrounding environments where they interact with the objects. Thus, they can be regarded as independent agents.
This conceptual independency, however, raises an ethical dilemma caused by the absence of legal ramification of AI.
Many researchers has been questioning whether or not these super-intelligent agents should have duties to the society and to what extent governments give social rights \cite{bob}.
Given that approach, \cite{kerb} mentions early speculations of social equality regarding civil and political rights among robots and humans in Japanese anime and mangas which artworks are %consisted of futuristic plots including robots cohabitating and interacting with humans.
\citeA{gre} discusses that it is not obvious that who will be responsible for results of AI's actions.
Not only does AI's position in the society matter, but it is also equally important for governments to decide the AI's responsibility for the society, vice versa.

\subsection{Socio-economic Issues}
The rise of computers which has led the employment of robots in industry lessen the human employment starting from late 70's.
Because of the downsizing tendency of corporations which resulted from this replacement, millions of low-skilled workers lost their jobs.
Given that fact, \citeA{gre} predicts the aftermath of the creation of AI.
This vast computation power might replace most of the low-skilled labourers with the more powerful robots.
In the light of that prediction, highly developed economies may show an extensive recession. \par
Along with the economical effects of workplace computerization, eradication of low-skilled jobs may lead the expansion of the gap among the social groups.
For instance, those who can use computers or know develop software have reached to higher classes in the societies.
This expansion of gap among the social groups contradicts the societal goals of the creation of AI. \par
In addition to former arguments, \citeA{rosa} proposes yet another.
Even though researchers, for instance, want to create a narrow-domain savvy robot, the robot may want to change its profession from the one that it had been taught or coded to a brand new one.
This probable change of profession contradicts with the reason its creation purpose which may be interpreted as a act of disobey to its master.

@@

This discrepancy brings about a major problem at the individual and societal levels.
One example of this fact is that individuals have started to get strong advice from AI applications, a software crunching numbers faster than a man can do, rather than a close friend who might know better about the individual seeking advice, such as the taste in music or book.
Even though this issue seems to have a minor flipside, once it is aggregated \citeA{lan} claims, it will create true alienation from society and confusion regarding personhood.
In other words, roboticists have not been able  to reach a consensus on the definition of robots the embodiment of AI, \citeA{lin} noted.
\par

>>>>

\subsection{Legal and Ethical Issues}
Robots are envisioned to be controlled by a such intelligence which enable their to perceive their surrounding environments where they interact with the objects by themselves. Thus, they can be regarded as independent agents.
This conceptual freedom, however, raises an ethical dilemma caused by the absence of legal ramifications of AI.
\citeA{gre} examine that ambiguity by posing a controversial question: "Who will be responsible for results of AI's actions and failure?"
Since the contemplation of AI and robots indicates that robots will supposedly make their own choices take actions according to these choices, another interesting question arises: "Would robots be prosecuted -maybe executed- because of the fails they commit?"
Similar to the questions above, there are many questions that governments need to address by creating regulations and laws under which robots will be positioned. \par
Furthermore, many researchers has been questioning whether or not these super-intelligent agents should have duties to society; if so, to what extent governments should give social rights to robots. \citeA{bob} addresses this issue by underlining basic rights and duties of citizens such as taxing and voting.
In other words, not only does AI's legal ramification matter, but it is also equally important for governments to decide the AI's responsibility for the society, vice versa.
To address this issue, \citeA{kerb} analyzes Japanese artworks showing futuristic plots based upon robots cohabitating and interacting with humans.
These artworks depicts the very early speculations of social equality between man and machine regarding civil and political rights among.
Kerb's evaluation of these artworks concludes that robots, depicted and envisioned in the artworks, are neither overlords nor serf-laborers.

\subsection{Socio-economic Issues}
The rise of computers which has led the employment of robots in industry lessen the human employment starting from late 70's.
Because of the downsizing tendency of corporations which resulted from this replacement, millions of low-skilled workers lost their jobs.
Given that fact, \citeA{gre} predicts the aftermath of the creation of AI.
This vast computation power might replace most of the low-skilled labourers with the more powerful robots.
In the light of that prediction, highly developed economies may show an extensive recession. \par

Along with the economical effects of workplace computerization, eradication of low-skilled jobs may lead the expansion of the gap among the social groups.
For instance, those who can use computers or know develop software have reached to higher classes in the societies.
This expansion of gap among the social groups contradicts the societal goals of the creation of AI. \par

% Personal robots personhood problem.

@@

This discrepancy brings about a major problem at the individual and societal levels.
One example of this fact is that individuals have started to get strong advice from AI applications, a software crunching numbers faster than a man can do, rather than a close friend who might know better about the individual seeking advice, such as the taste in music or book.
Even though this issue seems to have a minor flipside, once it is aggregated \citeA{lan} claims, it will create true alienation from society and confusion regarding personhood.
In other words, roboticists have not been able  to reach a consensus on the definition of robots the embodiment of AI, \citeA{lin} note.
\par
